Ground state energy of quantum dots using the coupled cluster method

### 2018-04-30 project_2/article/article.tex
Move references after appendix
Add spin-deltas

            The normalization condition now reads
            \begin{align}
                \braket{\alpha}{\beta} = \delta_{\alpha\beta},
            \end{align}
            when $\ket{\alpha}$ and $\ket{\beta}$ share the same spin direction.
            The one-body matrix will now be a diagonal matrix with the
            eigenenergies of single particle harmonic oscillator functions as
            elements.
            \begin{align}
                \bra{\alpha}h\ket{\beta} = \epsilon_{\beta}\delta_{\alpha\beta}.
            \end{align}

>>>>

            The normalization condition now reads
            \begin{align}
                \braket{\alpha}{\beta}
                = \delta_{\alpha\beta}\delta_{\sigma_\alpha\sigma_\beta},
            \end{align}
            The one-body matrix will now be a diagonal matrix with the
            eigenenergies of single particle harmonic oscillator functions as
            elements.
            \begin{align}
                \bra{\alpha}h\ket{\beta}
                = \epsilon_{\beta}
                \delta_{\alpha\beta}\delta_{\sigma_\alpha\sigma_\beta}.
            \end{align}
